### 2020-08-31 benchmarking/benchmarkingVM/ESS_round5.tex
Results update

% Created by tikzDevice version 0.12.3.1 on 2020-08-29 17:56:05
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (289.08,323.19) {\bfseries Comparison of AVMVN+NER+Bactrian+adapt(\textit{real}) and NER+Bactrian+adapt(\textit{real})};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 21.60,178.67) {Relative ESS/hr};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (518.16,297.33);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 60.00,178.67) -- (518.16,178.67);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.87,182.29) --
	( 65.87,155.40);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 65.87,164.96) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.75,182.37) --
	( 71.75,172.85);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 71.75,173.72) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.62,206.63) --
	( 77.62,183.55);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 77.62,191.20) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.50,192.35) --
	( 83.50,184.14);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 83.50,184.36) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.37,198.03) --
	( 89.37,169.64);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 89.37,179.94) {$p$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.24,194.87) --
	( 95.24,123.63);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 95.24,155.36) {$p$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.12,195.10) --
	(101.12,177.27);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (101.12,182.29) {$p$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.99,193.21) --
	(106.99,172.45);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (106.99,178.95) {$p$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.86,199.27) --
	(112.86,173.64);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (112.86,182.57) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 65.87,180.93) --
	(118.74,180.93);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.31,275.05) {1.1\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (124.61,  0.00) --
	(124.61,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.49,204.32) --
	(130.49,182.55);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (130.49,188.58) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.36,199.93) --
	(136.36,178.39);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.36,184.30) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.23,195.23) --
	(142.23,183.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (142.23,184.70) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.11,217.30) --
	(148.11,203.38);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.11,205.48) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.98,248.47) --
	(153.98,227.05);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.98,232.90) {$L$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.86,183.36) --
	(159.86,156.04);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.86,164.84) {$L$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.73,231.86) --
	(165.73,219.25);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.73,220.70) {$L$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.60,235.33) --
	(171.60,157.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.60,191.36) {$L$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.48,199.47) --
	(177.48,168.81);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.48,179.28) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (130.49,199.54) --
	(183.35,199.54);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (156.92,275.05) {11\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (189.22,  0.00) --
	(189.22,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.10,173.48) --
	(195.10,158.53);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.10,161.15) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.97,184.98) --
	(200.97,182.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.97,178.86) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.85,186.09) --
	(206.85,182.08);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.85,179.23) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,194.39) --
	(212.72,191.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.72,188.11) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.59,208.43) --
	(218.59,201.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (218.59,199.93) {$r$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.47,185.90) --
	(224.47,183.69);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (224.47,179.94) {$r$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.34,200.46) --
	(230.34,196.65);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (230.34,193.69) {$r$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.22,188.37) --
	(236.22,184.80);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (236.22,181.72) {$r$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.09,174.48) --
	(242.09,171.48);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (242.09,168.12) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (195.10,186.05) --
	(247.96,186.05);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (221.53,275.05) {3.7\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (253.84,  0.00) --
	(253.84,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.71,170.83) --
	(259.71,145.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (259.71,153.29) {$l$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (265.58,217.60) --
	(265.58,197.77);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (265.58,202.82) {$l$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.46,235.98) --
	(271.46,197.45);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (271.46,211.85) {$l$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.33,200.90) --
	(277.33,186.58);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (277.33,188.88) {$l$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.21,194.62) --
	(283.21,161.91);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (283.21,173.40) {$l$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (289.08,195.59) --
	(289.08,178.65);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (289.08,182.26) {$l$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (294.95,222.46) --
	(294.95,190.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (294.95,201.82) {$l$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (300.83,227.18) --
	(300.83,192.62);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (300.83,205.04) {$l$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.70,227.56) --
	(306.70,211.98);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (306.70,214.91) {$l$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (259.71,197.56) --
	(312.58,197.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (286.14,275.05) {9.6\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (318.45,  0.00) --
	(318.45,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.32,177.22) --
	(324.32,147.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (324.32,159.08) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.20,189.14) --
	(330.20,175.54);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (330.20,178.84) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.07,201.86) --
	(336.07,178.01);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (336.07,186.44) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.94,197.85) --
	(341.94,176.63);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (341.94,183.74) {$\sigma$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.82,185.47) --
	(347.82,162.39);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (347.82,170.43) {$\sigma$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.69,171.36) --
	(353.69,145.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (353.69,154.73) {$\sigma$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.57,218.64) --
	(359.57,189.11);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (359.57,200.38) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.44,197.28) --
	(365.44,169.92);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (365.44,180.10) {$\sigma$};
\definecolor{drawColor}{RGB}{68,68,68}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (301.08,335.19) {\bfseries Comparison of AVMVN+NER+Bactrian+adapt(\textit{real}) and NER+Bactrian+adapt(\textit{real})};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  9.60,190.67) {Relative ESS/hr};
\end{scope}
\begin{scope}
\path[clip] ( 48.00, 60.00) rectangle (554.16,321.33);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
	(474.88,173.19);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.10,170.57) --
	( 54.10,160.89);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 54.10,165.73) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.20,193.03) --
	( 60.20,169.27);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 60.20,181.15) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.29,191.40) --
	( 66.29,174.61);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] ( 66.29,183.01) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.39,196.48) --
	( 72.39,170.97);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] ( 72.39,183.73) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49,141.00) --
	( 78.49, 76.27);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] ( 78.49,108.63) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.59,183.38) --
	( 84.59,168.50);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] ( 84.59,175.94) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.69,170.18) --
	( 90.69,143.82);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] ( 90.69,157.00) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.79,196.84) --
	( 96.79,181.84);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] ( 96.79,189.34) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 54.10,169.09) --
	(102.88,169.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.49,284.14) {-1.5\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (108.98,  0.00) --
	(108.98,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.08,194.11) --
	(115.08,179.13);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (115.08,186.62) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.18,185.55) --
	(121.18,175.29);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (121.18,180.42) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.28,214.73) --
	(127.28,201.99);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (127.28,208.36) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.38,249.42) --
	(133.38,231.42);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (133.38,240.42) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47,159.92) --
	(139.47,140.75);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (139.47,150.33) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.57,214.01) --
	(145.57,205.08);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (145.57,209.54) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,200.10) --
	(151.67,107.60);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (151.67,153.85) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.77,178.44) --
	(157.77,154.84);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (157.77,166.64) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (115.08,188.55) --
	(163.87,188.55);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.47,284.14) {5.7\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (169.97,  0.00) --
	(169.97,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.06,172.66) --
	(176.06,170.84);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (176.06,171.75) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.16,169.79) --
	(182.16,167.75);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (182.16,168.77) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.26,189.75) --
	(188.26,187.44);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (188.26,188.59) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,203.19) --
	(194.36,199.69);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (194.36,201.44) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46,171.28) --
	(200.46,169.79);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (200.46,170.53) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.56,184.57) --
	(206.56,182.27);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (206.56,183.42) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.65,163.32) --
	(212.65,160.43);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (212.65,161.87) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.75,155.78) --
	(218.75,154.17);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (218.75,154.97) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.06,175.53) --
	(224.85,175.53);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.46,284.14) {0.84\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (230.95,  0.00) --
	(230.95,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,218.83) --
	(237.05,206.46);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (237.05,212.65) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.15,242.97) --
	(243.15,220.02);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (243.15,231.49) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.24,208.35) --
	(249.24,192.32);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (249.24,200.33) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.34,176.56) --
	(255.34,142.47);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (255.34,159.52) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,187.62) --
	(261.44,174.61);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (261.44,181.12) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.54,206.77) --
	(267.54,181.77);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (267.54,194.27) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.64,229.57) --
	(273.64,209.79);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (273.64,219.68) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.74,216.31) --
	(279.74,206.19);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (279.74,211.25) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.05,202.10) --
	(285.83,202.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (261.44,284.14) {11\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (291.93,  0.00) --
	(291.93,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.03,209.96) --
	(298.03,198.22);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (298.03,204.09) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.13,238.47) --
	(304.13,217.31);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (304.13,227.89) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.23,204.06) --
	(310.23,189.08);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (310.23,196.57) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.33,171.91) --
	(316.33,144.86);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (316.33,158.38) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42,183.17) --
	(322.42,172.59);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (322.42,177.88) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.52,206.07) --
	(328.52,181.21);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (328.52,193.64) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.62,210.76) --
	(334.62,182.47);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (334.62,196.61) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.72,208.61) --
	(340.72,197.60);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (340.72,203.11) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.03,195.41) --
	(346.82,195.41);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (322.42,284.14) {8.3\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (352.92,  0.00) --
	(352.92,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,174.36) --
	(359.01,162.95);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (359.01,168.66) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.11,189.08) --
	(365.11,165.88);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (365.11,177.48) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.21,190.22) --
	(371.21,174.54);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (371.21,182.38) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.31,180.24) --
	(377.31,143.99);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (377.31,162.11) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41,146.90) --
	(383.41,126.33);
\definecolor{fillColor}{RGB}{0,219,171}
